---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# MetaCOVID Dataset

```{r setup, include = FALSE}
source(here::here("R", "prepare-trials-w-results.R"))

n_direcct_trials <- nrow(all_trials)

n_trials_w_results <- nrow(trials_w_results)

n_all_results <- nrow(results_from_trials)
  # trials_w_results_combined %>% 
  # select(starts_with("pub_type")) %>% 
  # tidyr::pivot_longer(everything()) %>% 
  # select(-name) %>% 
  # tidyr::drop_na() %>% 
  # nrow()

# Recode results
recoded_results <-
  results_from_trials %>% 
  mutate(pub_type =
           case_when(
             # tri00084/ChiCTR2000029542: application note of ~1000 words (10.1093/jmcb/mjaa014)
             id == "tri00084" ~ "other",
             
             # tri02189/NCT04399746: "other" is actually journal article (https://www.biomedres.info/biomedical-research/effects-of-ivermectinazithromycincholecalciferol-combined-therapy-on-covid19-infected-patients-a-proof-of-concept-study-14435.html)
             id == "tri02189" ~ "full_results_journal_article",
             TRUE ~ pub_type
           )
  )

n_summary_results <-
  recoded_results %>% 
  filter(pub_type == "summary_results") %>% 
  nrow()

n_other_results <-
  recoded_results %>% 
  filter(pub_type == "other") %>% 
  nrow()

# Screen results
screened_results <-
  recoded_results %>% 
  
  filter(!pub_type %in% c("summary_results", "other")) %>% 
  
  # tri00107/ChiCTR2000029381: non-english result publication (10.3760/cma.j.cn121430-20200406-00386)
  # tri00732/NCT04261517: non-english result publication (10.3785/j.issn.1008-9292.2020.03.03)
  # tri02562/NCT04332081: final version not accessible (10.22462/01.03.2020.1), but pre-proof found via semantic scholar: https://www.uhms.org/images/UHM-Journal/PRE-PROOF_-_HBO2_for_COVID_-_47-3_THIRD_QUARTER_2020_print_version_version_47-3.pdf
  # https://www.semanticscholar.org/paper/Hyperbaric-oxygen-therapy-for-COVID-19-patients-Gorenstein-Castellano/fc4bab1af1dfe771cac56ad2c5b42df67096f6c6
  filter(!id %in% c("tri00107", "tri00732", "tri02562"))

n_screened_results <- nrow(screened_results)

# Spread results wide (i.e., one row per trial)
screened_results_wide <-

  screened_results %>%

  select(-trn, -search_type, -search_engine, comments_results = comments) %>%

  # Add result number by trial
  group_by(id) %>%
  mutate(n_result = row_number()) %>%
  ungroup() %>%

  # Pivot to 1 row per trial (multiple results)
  tidyr::pivot_wider(id,
              names_from = n_result,
              values_from = c(pub_type,
                              doi,
                              pmid,
                              cord_id,
                              url,
                              date_publication,
                              date_completion,
                              comments_results
              )
  ) %>%

  # Reorder columns so that grouped by result number
  relocate(any_of(ends_with(stringr::str_c(1:5))))

# Prepare metacovid trials with results and registrations
metacovid_trials <-
  screened_results_wide %>% 
  left_join(trials_w_results, by = "id") %>%
  left_join(registrations, by = "id") %>%
  arrange(id)

n_metacovid_trials <- nrow(metacovid_trials)

write_csv(trials_w_results_combined, paste0(dir_data, "/metacovid-trials.csv"))
```

## Study selection

The source dataset included `r n_direcct_trials` trials. We excluded `r n_direcct_trials - n_trials_w_results` trials without results. For the `r n_trials_w_results` trials with results, we screened all `r n_all_results` results to verify the publication types. We found one result (trial: NCT04399746) denoted as "other" in the source dataset which was actually a full-results journal article, and one result (trial: ChiCTR2000029542) denoted as a "full-results journal article" in the source dataset which was a "application note" and which we recoded as "other." After recoding these two results, we then excluded all summary results (n = `r n_summary_results`) and other results (n = `r n_other_results`), which included grey literature, conference abstracts and presentations, research letters and notes, etc. We also excluded two non-English results (trials: ChiCTR2000029381 and NCT04261517) and one result for which we could not access the full-text publication (trial: NCT04332081). Our analysis dataset comprised `r n_metacovid_trials` trials with `r n_screened_results` results.

## Screening criteria

Inclusion criteria:

-   Full or interim results, journal article or preprint
-   English-language publication
-   Full-text accessible

Exclusion criteria:

-   Summary results
-   Other results, such as grey literature, research letters and notes, etc. (categorized as "other" publication type in DIRECCT dataset)
